---
title: "Research Methodology - Panel Data Approaches"
author: "Lai Xiang"
date: "2026-01-20"
format: html
bibliography: references.bib
---

## Econometric Framework {#sec-methodology}

### Panel Data Model

We estimate the following fixed-effects specification:

$$
Y_{it} = \alpha_i + \gamma_t + \beta_1 T_{it} + \beta_2 T_{it}^2 + \beta_3 P_{it} + \mathbf{X}_{it}'\delta + \varepsilon_{it}
$$

where:

- $Y_{it}$ is log GDP per capita for country $i$ in year $t$
- $T_{it}$ is the population-weighted average temperature
- $P_{it}$ is total precipitation
- $\mathbf{X}_{it}$ is a vector of control variables
- $\alpha_i$ and $\gamma_t$ are country and year fixed effects

### Identification Strategy

```{r}
#| label: model-estimation
#| eval: false

# Two-way fixed effects estimation
model_fe <- feols(
  log_gdppc ~ temperature + I(temperature^2) + precipitation |
    country + year,
  data = panel_data,
  cluster = ~country
)

# Long-differences specification
model_ld <- feols(
  d_log_gdppc ~ d_temperature + d_temperature_sq |
    region,
  data = long_diff_data,
  cluster = ~country
)
```

### Robustness Checks

We conduct several robustness analyses:

1. **Alternative temperature measures**: Growing-degree days, heating/cooling degree days
2. **Spatial correlation**: Conley standard errors with varying distance cutoffs
3. **Non-linear specifications**: Spline regression, binned temperature categories
4. **Sample restrictions**: Excluding oil exporters, small island states

### Climate Projections

Future projections use CMIP6 ensemble under SSP2-4.5 and SSP5-8.5 scenarios.

```{r}
#| label: projection-setup
#| eval: false

scenarios <- c("ssp245", "ssp585")
gcm_models <- c("GFDL-ESM4", "IPSL-CM6A-LR", "MPI-ESM1-2-HR",
                 "MRI-ESM2-0", "UKESM1-0-LL")

project_damages <- function(scenario, model) {
  delta_t <- load_projections(scenario, model)
  damages <- predict(model_fe, newdata = delta_t)
  return(damages)
}
```
